
%%%%%%%%% Summary blocks

%%% You can type this much:

%{Recently graduated with a Master of Science in Robotics Engineering degree and significant ROS expertise on multiple projects with C++, and Python. Track record of quickly gaining enough proficiency on unfamiliar, complex systems to diagnose, improve and maintain robots and software stacks. Worked on the humanoids Valkyrie R5 and Baxter, as well as several mobile bases while developing hardware drivers and control software on ROS, as well as several robot interfaces using Qt and librviz with C++11. Developed applications of SLAM, machine learning, and computer vision mainly with }
 %%%%%%
 
\newcommand{\sumRobo}{ Robotics Engineer recently graduated with a Master's degree and significant ROS, C++, and Python expertise. Track record of quickly gaining enough proficiency on unfamiliar, complex systems to diagnose, improve and maintain robots and software stacks.}

\newcommand{\sumRoboB}{Robotics Engineer, MSc. Designed 
 and maintained robotic systems; implemented computer vision, navigation, mapping, control, and autonomy modules with ROS and OpenCV. Developed web, mobile, and desktop interfaces.  Prototyped automotive-grade enclosures and harnesses. Actively participated in research and education in my field. Familiar with development in batteries, actuators, and materials.
I value having a breadth of knowledge both in and out of my discipline. Looking forward to taking on newer challenges with an ambitious and diverse team of designers and innovators.
} 

\newcommand{\sumBlk}{Robotics Engineer (MSc), 
 and blockchain developer with demonstrated experience in system design \& lifecycle, and open-source development. Designed 
 and maintained advanced robotic systems; implemented computer vision, navigation, mapping, control, and autonomy modules with ROS and OpenCV.
 In the past three years, I brought my systems engineering and computer science expertise to distributed ledgers; improving smart contracts, developing dApps, and designing tokenomic models.
 Looking forward to bringing hardware, software, and distributed systems together with an enthusiastic team.
} 

\newcommand{\SumAuto}{ Recently graduated Master Software Engineer focused on Robotics and autonomous mobile systems. Proven hands-on experience developing CAN interfaces, computer vision, and AI software.}

\newcommand{\SumVR}{ Recently graduated Software Engineer with GUI, VR  and 3D graphic design experience. Proficient in APIs like Qt, OpenCV, and Unity.  Improved ROSJava libraries and developed an Android VR app for the Robotics field.}

\newcommand{\sumRoboDetailed}{Recently graduated with a Master of Science in Robotics Engineering degree and significant ROS expertise on multiple projects with C++, and Python. Track record of quickly gaining enough proficiency on unfamiliar, complex systems to diagnose, improve and maintain robots and software stacks. Worked on the humanoids Valkyrie R5 and Baxter, as well as several mobile bases while developing hardware drivers and control software on ROS, as well as several robot interfaces using Qt and librviz with C++11. Developed applications of SLAM, machine learning, and computer vision mainly with OpenCV and TensorFlow. }

%%%%%%% Section 

