%\renewcommand{\initem}{\item}
%%select style
%flags for the section's formatting
%\let\cventry\cventrycompact
%\let\initem\initem

%myRide
%Secured company support for PhD funding
%Built the CAN control interface, perception system prototype and created the %product roadmap
%Successfully pitched the system prototype in live demonstrations


\newcommand{\rscs}{\cventry{May 2021 -- Dec 2022}{Robotics Engineer}{Radiation Safety \& Control Services}{Hampton, NH}{}{
\initem{Secured the company's financial endorsement for a PhD program in Robotics.}
\initem{Prototyped the CAN control interface, setup the hardware on an EV car.} 
\initem{Implemented the ROS network that consists of ROS-to-CAN, semantic segmentation, driving and camera modules on a Jetson TX2.}
\initem{Successfully live-demonstrated the product prototype for controls and perception to the investors.}}}


\newcommand{\auriel}{\cventry{Jun 2017}{Research Intern}{Auriel Capital Ltd.}{London, UK}{}{
\initem{Delivered market report analyzing the future of Robotics.}
\initem{Provided insights about challenges, key players and emerging technologies.}}}

\newcommand{\myride}{\cventry{May 2019 -- April 2021}{Systems Lead}{myRide}{Chelmsford, MA}{}{
\initem{Secured the company's financial endorsement for a PhD program in Robotics.}
\initem{Prototyped the CAN control interface, setup the hardware on an EV car.} 
\initem{Implemented the ROS network that consists of ROS-to-CAN, semantic segmentation, driving and camera modules on a Jetson TX2.}
\initem{Successfully live-demonstrated the product prototype for controls and perception to the investors.}}}

\newcommand{\hiro}{\cventry{Nov 2017 -- Jan 2019}{Lab Assistant}{Human-Inspired Robotics Lab}{Worcester, MA}{}{
\initem{Supervised graduate research and undergrad project teams that focus on teleoperation, mobile humanoids and perception.}
\initem{Created a VR headset app with ROSJava that views multiple USB cameras and is controlled with voice commands and desktop GUI (python, Qt) that records the user's stream.}%fix this one
\initem{Spearheaded the development of the lab's humanoid robot, while maintaining the hardware and managing the lab repository.} \initem{Designed control modules, robot software, and UIs for mobile and desktop with ROS.}}} %experiment software, user interface for desktop  and mobile ROSCpp, RosJava, VR!!

\newcommand{\technocopia}{\cventry{Sep 2017 -- May 2018}{Graduate Intern}{Technocopia, Worcester Think Tank}{Worcester, MA}{}{
\initem{Co-coached the youngest team in the regional First Lego League qualifications.}
\initem{Encouraged kids to collaborate and think creatively towards tackling technical challenges }
}}

\newcommand{\spark}{\cventry{Jul 2017 -- Aug 2017}{Graduate Assistant}{WPI, Amazon Robotics }{Worcester -- North Reading, MA}{}{\initem{Mentored elementary and middle school students in SPARK, Junior Robotics Challenge Program( at Amazon Robotics) and LAUNCH weekly Robotics camps.}
\initem{Coordinated Undergraduate assistants.}}
}

\newcommand{\bkg}{\cventry{Aug 2016 -- Present}{Technology Consultant}{\&BKG, MainScreen}{Istanbul, Turkey {\small(\textit{remote})}}{}{
\initem{Saved the company's entire Digital Out-of-home advertising budget by setting up an open-source system.}
\initem{Kick-started systems development for Real-time Bidding and programmatic sales for digital assets.}
\initem{Secured a partnership deal with a pioneering ad technology creator.}
}}
