\let\cventry\cventryproject
\cventry{Jul 2018 -- Feb 2019}{Perception Modalities and Effects on Motor Coordination and Learning
}{Human-Robot Interaction (HRI) 2019 Conference Submission}{WPI}{}{ Observed subject behavior under different perception scenarios that imitate robot cameras during teleoperation. Co-designed the experiment. Implemented Android VR and desktop software to view the cameras and record the active camera. \noindent  \hfill \textbf{Cont.}}
%cventry{June 2018 -- December 2018}{Teleoperation interface comparison of a mobile humanoid robot}{HRI 2019 Conference Submission}{WPI}{}{ Comparing haptic, motion capture and joystick inputs and user performance in tele-nursing tasks to evaluate each system's operation capacity and observe operational patterns. The outcome of the research will form the basis of our Shared Autonomy and Intent Inference papers. }


\cventry{Jan 2018 -- Mar 2018}{Fast Adaption of Movement Primitives through Integrated Online and Offline Imitation Learning Search}{IROS 2018 Conference Submission}{WPI}{}{ Prototyped a reconfigurable learning-from-demonstration system to carry out manipulation tasks with a human-like pose. Implemented the object detection and grasping capabilities, oversaw the complete robotic system and peripheral device support.}
\cventry{Jan 2018 -- Feb 2018}{}{AI Bass Drum Player with Beat Detection and Prediction }{Jetson Rocket Challenge}{}{Built a bass drum player that controls a stepper motor over I2C by detecting onsets in live audio input and predicting next beats real-time on a Jetson TX2 board. Implemented the AI Stack and the I2C controller as ROS packages and overhauled the mechanism.}
%cventry{Mar 2017 -- July 2017}{}{LSD-SLAM for Windows}{WPI}{}{ Ported Large-Scale Direct SLAM to Windows. After rebuilding the dependency tree, recovered the lost ROS message and node functionality using multithreading and UDP. Currently re-implementing the interface using PCL. }
\cventry{Aug 2016 -- Dec 2016}{}{Space Robotics Competition (SRC) - Capstone Design Project}{WPI}{}{Implemented color and object recognition and image to real world transformations on ROS (C++/Python) as well as handling system integrity and debugging full body control for SRC qualification tasks with Valkyrie R5. The team consisted of three people.}
%
\cventry{Aug 2015 -- May 2016}{}{WALRUS Rover Expansion - Major Qualifying Project (MQP)}{WPI}{}{ Enhanced disaster response robot WALRUS with 3D Simultaneous Localization and Mapping and GUI with 3rd person viewport features using ROS, Qt, and RViz. Reverse engineered the robot to debug drivers, fix CPU overflow and overheat issue while updating system diagnostics. Introduced multiple roslaunch configurations. Added Qt5 support using CMake. Was also responsible from engineering development, system management for Ubuntu, embedded systems, and drivers as well as version control in a team of three.}
%
\cventry{Jan 2015 -- Feb 2015}{}{Microplastic Pollution - Interactive Qualifying Project (IQP)}{Hong Kong}{}{Collected microplastic samples from multiple bays in HK and ran spectrometer analysis on them as a three-person group. Surveyed the locals about awareness on microplastic pollution.}
%
\cventry{}{\small *( Team size: Framework, Languages)}{Final Projects for Computer Vision, Robot Dynamics, Robot Control, Unified Robotics courses*}{WPI}{}{}{}{}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l@{\extracolsep{\fill}}r}%

Autonomous Path Planning for Differential Drive Robots & (4; MatLab, Java) & \textbf{Aug 2015 -- Dec 2015} \\
SLAM and Path Planning for TurtleBots & (2; ROS, Python) & \textbf{Mar 2014 -- May 2014} \\
Term paper on 2-DOF Gradient Control of Mobile Robots & (1; MatLab) & \textbf{Jan 2014 -- May 2014} \\
Automated 2-DOF Manipulator with Load Classification & (3; AVR, C) & \textbf{Jan 2014 -- Mar 2014} \\
Dynamic Force Controlled Robot on Vertical Surfaces & (3; Arduino, C) & \textbf{Oct 2013 -- Dec 2013} \\

\end{tabular*}
