%%%%%% Items %%%%%%

%%%%%%%%% Blockhain

\newcommand{\saintsB}{\cventry{Feb 2022 -- Present}{Co-founder}{THE 541N75}{Istanbul, Turkey}{}{ \initem{Created a DAO platform using a proxy 
 contract managing upgradable modules. }\initem{Mapped out tokenomics consisting of 
 utility, equity, and governance tokens with dynamic supply and controlled inflation. Designed modules including selective treasury, multi-tier governance, project tracking, merit-based membership, access NFTs, and income distribution.} \initem{Analyzed past three years' DeFi projects for tokenomics principles, contract structures, and dApp design.} \initem{  Supervised the collective's multiple creative and digital projects}. \initem{Mentored the team on software and hardware utilities, blockchain, and project management.}}}

\newcommand{\peraB}{\cventry{Dec 2021 -- Dec 2022}{Software Developer}{Pera Finance}{Istanbul, Turkey}{}{ \initem{Increased code efficiency utilizing  better data structures and Solidity features to eliminate most of the gas costs.}\initem{Designed the next version with customizable competitions created with a factory contract to support future modules and  other projects.\\}\initem{ Supervised the new social marketing campaign for a global audience while personally guiding on copyrighting and visual design.}}}
%%%%%%%%% Robo
 
\newcommand{\saints}{\cventry{Feb 2022 -- Present}{CTO}{THE 541N75}{Istanbul, Turkey}{}{ \initem{Designed the creative collective DAO that enables creators and investors to collaborate with treasury, governance, membership, and management modules.}\initem{Determined the startup's organizational structure,  bylaws, project pipelines, and community requirements.}\initem{Mentored members and projects on software (CGI, AI), hardware, and project management.}}}

\newcommand{\pera}{\cventry{Dec 2021 -- Dec 2022}{Lead Developer}{Pera Finance}{Istanbul, Turkey}{}{ \initem{Increased code efficiency of the first-ever DeFi trading competitions to eliminate most of the gas costs.}\initem{Designed the next version with customizable competitions created with a factory contract to support future modules and  other projects.}\initem{Oversaw copywriting and content creation together with a marketing agency, creating a social marketing campaign for a larger audience.}}}

\newcommand{\rscs}{\cventry{May 2020 -- Dec 2021}{Robotics Engineer}{Radiation Safety \& Control Services }{Hampton, NH}{}{ \initem{Converted a radiation-scanning cart into a robotic platform with live LIDAR-based SLAM, dynamic URDF model, and diagnostics. Updated the data collection model with continuous, automated binning and visualization.}\initem{Designed and built multiple sensor circuits for gas supply control for Arduino and Embedded PCs. }\initem{Designed a radiation source test unit with position control with an  rPI-controlled actuator, custom-boot Ubuntu and a web-based touchscreen interface.}}}

\newcommand{\myride}{\cventry{March 2019 -- April 2020}{Lead Systems Engineer}{myRide}{Chelmsford, MA}{}{ \initem{Implemented a drive-by-wire control system on KIA Soul EV using Arduino and Jetson boards, designed and prototyped the mechanical assembly, with designing most of the custom hardware and software.}\initem{Implemented vision and control modules on ROS,  improved controller firmware, and CAN interface.}\initem{Prototyped the controller enclosures, harnesses, interior panels, a gear-shifter, and the installation scheme.}\initem{Carried out investor presentations and screened potential hires.}}}


\newcommand{\hiro}{\cventry{Nov 2017 -- Feb 2019}{Lab Assistant}{Human-Inspired Robotics Lab, WPI}{Worcester, MA}{}{ \initem{Supervised graduate research and undergrad project teams that focus on teleoperation, mobile humanoids, and perception.}\initem{Implemented USB, mocap, and voice controllers for a ROS robotic platform as well as its workstation and embedded system.}\initem{Rewritten the system procedures to reduce training time to 2 hours from 9 with better user performance.}\initem{Implemented a multi-camera Android VR app with a companion Linux app to monitor perception experiments.}}}


\newcommand{\lego}{\cventry{Sep 2017 -- May 2018}{FLL Coach, Instructor}{Technocopia, Worcester Think Tank}{Worcester, MA}{}{ \initem{Co-coached the youngest team in the regional First Lego League qualifications, teaching robotics basics and focusing on how to approach engineering problems and design as a team.}}}


\newcommand{\launch}{\cventry{Jul 2017 -- Aug 2017}{Graduate Assistant}{Amazon Robotics, WPI}{North Reading, MA}{}{ \initem{Mentored elementary and middle school students in SPARK, Junior Robotics Challenge Program at Amazon Robotics and LAUNCH weekly Robotics camps and coordinated undergraduate instructors.}}}


\newcommand{\auriel}{\cventry{Jun 2017}{Research Intern}{Auriel Capital Ltd.}{London, UK (Remote)}{}{ \initem{Delivered a comprehensive report on the Robotics industry, highlighting the critical role of battery and motor technology in future trends.}}}


\newcommand{\bkgms}{\cventry{Aug 2016 -- Present}{Technology Consultant}{MainScreen}{Istanbul, Turkey (Hybrid)}{}{ \initem{Saved the entire outdoor signage budget by deploying an open-source system hosted on own servers with Ubuntu nodes.}}}



%%%%%%%%%%%%%% Section Body %%%%%%%%%%%%%%%%




